---
title: "Project 3: STAT302package Tutorial"
author: "Yi Sun, Yuxin Huang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 6, 
  fig.height = 5, 
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STAT302package)




set.seed(302)
```

```{r}
library(readr)
my_gapminder <- read_csv("../Data/my_gapminder.csv")
my_penguins <- read_csv("../Data/my_penguins.csv")
source("../Code/my_rf_cv.R")
```
## Tutorial for my_rf_cv


We will be using the function my_rf_cv to perform random forest cross-validation
in this tutorial. Our goal is to make predictions of body_mass_g using covariates bill_length_mm, bill_depth_mm, and flipper_length_mm. We choose three values for k: 2, 5, 10. For each
value of k, we will perform the random forest cross-validation 30 times and keep track
of the CV estimated MSE for each iteration.
<br>
```{r, fig.show = "hold"}
# the values of k
k_value <- c(2, 5, 10)



# create a list in advance, to keep track of the CV MSE
output_rf_cv <- list()

for (i in 1:length(k_value)) {
  # keep track of MSE for each iteration of the total 30 iterations
  MSE <- c(1:30)
  
  for (j in 1:30) {
    
    # use my_rf_cv to calculate the MSE
    MSE[j] <- STAT302package::my_rf_cv(k_value[i])
    
  }
  
  # store the MSE in the list
  output_rf_cv[[i]] <- MSE
 
}

# a vector of the average CV estimates for each k
mean_MSE <- c(mean(output_rf_cv[[1]]), mean(output_rf_cv[[2]]), mean(output_rf_cv[[3]]))
# a vector of the standard deviation of the CV estimates across k                  
sd_MSE <- c(sd(output_rf_cv[[1]]), sd(output_rf_cv[[2]]), sd(output_rf_cv[[3]]))
                                       
# create a data frame in order to build a table
my_df_rf <- data.frame(mean_MSE, sd_MSE)
rownames(my_df_rf) <- c("k = 2", "k = 5", "k = 10")
colnames(my_df_rf) <- c("mean of MSE", "standard deviation")

# create a table as the final output
my_table <- kableExtra::kable_styling(knitr::kable(my_df_rf))

# create a dataframe of the 30 MSE for each value of k
result <- data.frame(output_rf_cv[[1]], output_rf_cv[[2]], output_rf_cv[[3]])
colnames(result) <- c("k = 2", "k = 5", "k = 10")


```

<br>

From the tabe above, we can see that both the means of CV MSE and the standard deviations of CV MSE
decrease as the value of k increases. This is because when the value of k increases, our predictions get 
more accurate and the test errors decreases. Therefore, CV MSE minimized at k = 10.

<br>

```{r, fig.show = "hold"}

# create a vector representing the 30 iterations
iteration <-  cut(c(1:30), breaks = c(0, 10, 20, 30), 
                    labels = c("0-10", "10-20", "20-30"))

# create a data frame in order to make a box-plot of k = 2
graph1_data <- data.frame(output_rf_cv[[1]], iteration)
colnames(graph1_data) <- c("MSE", "iteration")
# plot the "MSE vs. Iterations" graph for k = 2
graph1 <- ggplot2::ggplot(data = graph1_data, 
             ggplot2::aes(x = iteration, y = MSE, group = iteration)) +
  
             ggplot2::geom_boxplot(size = 1, color = "cornflowerblue" ) +
    
             # set up the title of the graph
             # lable the two axes
             ggplot2::labs(title = "Estemiated CV MSE when k = 2",
             x = "Number of Iterations", y = "MSE") +
    
             # change background color to black and white
             ggplot2::theme_bw(base_size = 20) +
  
             # adjusting the size of the main title and its position
             # adjust the size of titles of axes
             ggplot2::theme(plot.title = ggplot2::element_text(size=20, hjust = 0.5), 
              axis.title.x = ggplot2::element_text(size = 18),
              axis.title.y = ggplot2::element_text(size = 18))



# create a data frame in order to make a box-plot of k = 5
graph2_data <- data.frame(output_rf_cv[[2]], iteration)
colnames(graph2_data) <- c("MSE", "iteration")
# plot the "MSE vs. Iterations" graph for k = 5
graph2 <- ggplot2::ggplot(data = graph2_data, 
            ggplot2::aes(x = iteration, y = MSE, group = iteration)) +
  
            ggplot2::geom_boxplot(size = 1, color = "cornflowerblue" ) +
    
            # set up the title of the graph
            # lable the two axes
            ggplot2::labs(title = "Estemiated CV MSE when k = 5",
            x = "Number of Iterations", y = "MSE") +
    
            # change background color to black and white
            ggplot2::theme_bw(base_size = 20) +
  
            # adjusting the size of the main title and its position
            # adjust the size of titles of axes
            ggplot2::theme(plot.title = ggplot2::element_text(size=20, hjust = 0.5), 
              axis.title.x = ggplot2::element_text(size = 18),
              axis.title.y = ggplot2::element_text(size = 18))



# create a data frame in order to make a box-plot of k = 10
graph3_data <- data.frame(output_rf_cv[[3]], iteration)
colnames(graph3_data) <- c("MSE", "iteration")
# plot the "MSE vs. Iterations" graph for k = 5
graph3 <- ggplot2::ggplot(data = graph3_data, 
            ggplot2::aes(x = iteration, y = MSE, group = iteration)) +
  
            ggplot2::geom_boxplot(size = 1, color = "cornflowerblue" ) +
    
            # set up the title of the graph
            # lable the two axes
            ggplot2::labs(title = "Estemiated CV MSE when k = 10",
            x = "Number of Iterations", y = "MSE") +
    
            # change background color to black and white
            ggplot2::theme_bw(base_size = 20) +
  
            # adjusting the size of the main title and its position
            # adjust the size of titles of axes
            ggplot2::theme(plot.title = ggplot2::element_text(size=20, hjust = 0.5), 
              axis.title.x = ggplot2::element_text(size = 18),
              axis.title.y = ggplot2::element_text(size = 18))

```
<br>
<br>

The above three boxplots show the CV estimated MSE of 30 iterations for k = 2, 5, 10.
We can see that k = 2 has the highst MSE and medians of MSE, and the MSE of k = 10 are 
relatively lower. Therefore, CV MSE decreases as the value of k increases and CV MSE is 
minimized at k = 10.

<br>

```{r}
library(ggplot2)
# save the three boxplots
ggsave(filename = "graph1.jpeg", plot = graph1, device = "jpeg", path = "../Output/Figures")
ggsave(filename = "graph2.jpeg", plot = graph2, device = "jpeg", path = "../Output/Figures")
ggsave(filename = "graph3.jpeg", plot = graph3, device = "jpeg", path = "../Output/Figures")


```

```{r}

# save the table as a .rds file
saveRDS(my_table, "Summary_Statistics.rds")


```


```{r}
# save the 90 simulated results as a .csv file 
write_csv(result, "90_simulated_results.csv")
```
